---
title: "methods.string"
author: "Erik Johnson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette illustrates how to use the methods.string package. Currently the methods.string package focuses on address explosion and cleaning.

```{r setup}
library(methods.string)
library(data.table)
library(knitr)
data(abbrev)
data(study.cities)

DT <- data.table(street = c('15408-10 16th Street, Units 1A-B', '2400 Midway Boulevard'), cityStateZip = c('Dever, Colorada, 80206', 'Denaver, CO'))
DT.explode <- explode.address(DT, study.cities)
```

## explode.address
Cleans and formats street and explodes to parts (uses. clean.street, clean.street.num, clean.street.unit)
Assume DT is a data.table as follows:
```{r, results='asis', echo=FALSE }
kable(DT)
```

Notice that there are numerous misspellings and street numbers can take a variety of ranges. Using the methods.string function \texttt{explode.address} cleans and explodes the addresses into component parts. 

```{r, results='asis', echo=FALSE }
kable(DT.explode)
```



